---
title: "Analysis"
author: "Stuart Miller, Paul Adams, Rikel Djoko"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, setup_, echo=FALSE, message=FALSE}
library(pwr2)
library(tidyverse)
```

# Power Analysis

The power analysis for this project was done using R package (pwr2).

https://cran.r-project.org/web/packages/pwr2/pwr2.pdf


```{r, power_analysis}

pwr.2way(a=2,
         b=2,
         alpha=0.05,
         size.A=90,
         size.B=90,
         f.A=NULL,
         f.B=NULL,
         delta.A=2,
         delta.B=2,
         sigma.A=4,
         sigma.B=6)
```


# Results of Study

```{r, load_data, echo=FALSE}
data <- read_csv('./results.csv',
                 col_types = cols(
                   schema = col_factor(levels = c('1','0')),
                   block_size = col_factor(levels = c('64','128','256')),
                   server_num = col_factor(levels = c('3','5')),
                   time = col_double()
                 )
        )

data$server_num <- recode(data$server_num, '3' = 'three_nodes', '5' = 'five_nodes')
data$schema <- recode(data$schema, '1' = 'normalized', '0' = 'denormalized')
```

```{r}
data %>% 
  group_by(schema) %>% 
  summarise(mean_time = mean(time),
            median_time = median(time),
            IQR_time = IQR(time),
            std_dev = sd(time),
            varaince = var(time))
```


## Summary Stats for the Levels

This is assuming that schema is the main driving factor of variation.

```{r, summary_stats, echo=FALSE}
grouped <- data %>% 
  group_by(server_num,schema) %>% 
  summarise(mean_time = mean(time),
            median_time = median(time),
            IQR_time = IQR(time),
            std_dev = sd(time),
            varaince = var(time))
grouped
```

## 2-Way ANOVA Profile Plot

```{r}
ggplot(data = grouped, aes(y = mean_time, x = block_size, color = schema)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean_time - sqrt(variance), ymax = mean_time + sqrt(variance)), width = .1) +
  facet_grid( ~ server_num) + 
  xlab('HDFS Block Size (MB)') +
  ylab('Query Time (seconds)') +
  ggtitle('Query Time for Schemas, MapReduce Block Size, and Cluster Size')
```







## 2-Way ANOVA Profile Plot

Profile plot is colored by schema.

```{r, profile_plot, echo=FALSE}
mysummary<-function(x){
  result<-c(length(x),mean(x),sd(x),sd(x)/length(x),min(x),max(x),IQR(x))
  names(result)<-c("N","Mean","SD","SE","Min","Max","IQR")
  return(result)
}

sumstats<-aggregate(time ~ schema:block_size, data = data, mysummary)
sumstats<-cbind(sumstats[,1:2],sumstats[,-(1:2)])

ggplot(sumstats, aes(x = block_size, y = Mean, group = schema, color = schema)) +
  ylab("Query Time (seconds)") +
  xlab("MapReduce Block Size (MB)") +
  ggtitle('Query Time for Schemas and MapReduce Block Size') +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = .1) +
  facet_grid( ~ schema)

sumstats
```



## Fit the ANOVA on the Data

This assumes data replication with schema as the primary source of variation.

```{r, anova, echo=FALSE}
analysis.aov <- data %>% 
  aov(time ~ schema + Error(block_size/schema), data = .)

aov.summ <- summary(analysis.aov)
aov.summ
```

## Plot Multiple Comparisons



```{r, mult_compare, echo=FALSE}
analysis.aov <- data %>% 
  aov(time ~ schema:block_size, data = .)

with(par(mai=c(1,2.5,1,1)),
     {plot(TukeyHSD(analysis.aov),
           las=1,
           cex.axis=0.4)
       }
     )
```






